### 2007-11-08 Documentation/Manual.tex
Another test

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{ae,aecompl} % only for Type 1 fonts for readable pdf convert

\newcommand{\glbxxx}{hep-ph/0407333}
\newcommand{\glbxxxtwo}{hep-ph/XXYYZZZ}
\newcommand{\capdef}{}
\newcommand{\mycaption}[2][\capdef]{\renewcommand{\capdef}{#2}%
        \caption[#1]{{ %\itshape
 {\footnotesize #2}}}}
\makeatletter
\renewcommand{\fnum@table}{\textbf{\tablename~\thetable}}
\renewcommand{\fnum@figure}{\textbf{\figurename~\thefigure}}
\makeatother

@@

\GLOBES\ is developed for academic use. Thus, the \GLOBES\ Team would
appreciate being given academic credit for it. Whenever you use \GLOBES\
to produce a publication or a talk indicate that you have used \GLOBES\ and
please cite the following references~\cite{globes_paper,globes_paper_two}
\begin{quote}
P. Huber, M. Lindner and W. Winter\\
Simulation of long baseline neutrino oscillation experiments with \GLOBES\\
Comput. Phys. Commun. 167 (2005) 195, arXiv:\glbxxx,
\end{quote}

\begin{quote}
P. Huber, J. Kopp, M. Lindner, M. Rolinec, and W. Winter\\
TO BE DEFINED, NEEDS TO BE UPDATED [WW]\\
arXiv:\glbxxxtwo,
\end{quote}
but \emph{not} this manual. This manual itself is not a scientific 
publication and will not be submitted to a scientific journal. 
It will evolve during time since it is intended for 
regular revision. Besides that, many of the data which are used by \GLOBES\ 
and distributed together with it should be properly referenced. 
For details see below.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{ae,aecompl} % only for Type 1 fonts for readable pdf convert; may not be necessary anymore!

\newcommand{\glbxxx}{hep-ph/0407333}
\newcommand{\glbxxxtwo}{hep-ph/0701187}
\newcommand{\capdef}{}
\newcommand{\mycaption}[2][\capdef]{\renewcommand{\capdef}{#2}%
        \caption[#1]{{ %\itshape
 {\footnotesize #2}}}}
\makeatletter
\renewcommand{\fnum@table}{\textbf{\tablename~\thetable}}
\renewcommand{\fnum@figure}{\textbf{\figurename~\thefigure}}
\makeatother

@@

\GLOBES\ is developed for academic use. Thus, the \GLOBES\ Team would
appreciate being given academic credit for it. Whenever you use \GLOBES\
to produce a publication or a talk indicate that you have used \GLOBES\ and
please cite the following references~\cite{globes_paper,globes_paper_two}
\begin{quote}
P. Huber, M. Lindner and W. Winter\\
Simulation of long baseline neutrino oscillation experiments with \GLOBES ,\\
Comput. Phys. Commun. 167 (2005) 195, arXiv:\glbxxx,
\end{quote}

\begin{quote}
P. Huber, J. Kopp, M. Lindner, M. Rolinec, and W. Winter\\
 New features in the simulation of neutrino oscillation experiments with \GLOBES~3.0,
arXiv:\glbxxxtwo,
\end{quote}
but \emph{not} this manual. This manual itself is not a scientific 
publication and will not be submitted to a scientific journal. 
It will evolve during time since it is intended for 
regular revision. Besides that, many of the data which are used by \GLOBES\ 
and distributed together with it should be properly referenced. 
For details see below.
